---
title: "Generation time"
output: html_document
---

```{r Load packages and functions}
require(tidyr)
require(dplyr)
require(rstan)
require(brms)
library(AGHmatrix)
library(hglm)
require(arm)
```

```{r read data and further manipulations, include=FALSE}
d3<-read.csv("/home/yi/Dropbox/GT/Resubmission/Resubmission3/Data_Code/d.csv")

d4<-d3[]
d4$age[d4$age>6]<-6
d4$age2<-as.factor(d4$age)
d4$flok2<-as.numeric(as.factor(d4$flok))
d4$agen<-d4$age + 1

d3m<-d4[d4$adsex==1,]
d3f<-d4[d4$adsex==2,]

dI<-read.csv("dI.csv")

ped <- read.table("ped.txt", header = T, stringsAsFactors = F)
ped[is.na(ped)]<-"0"
A  <- Amatrix(ped)

dIM<-read.csv("dIM.csv")
dFY2<-read.csv("dFY.csv")
dc2<-read.csv("CaptureHistories.csv")

```

The analyses of this paper is based on different data sets.
d3 is a the data set containing the data for the recruit production and survival to the next year for each individual at each age.

```{r Descriptive statistics data set 1}
#Number of individuals
length(levels(droplevels(d3$ringnr)))

##Number of individual breeding seasons
nrow(d3)

#Number of males and females
table(d3$adsex[-which(duplicated(d3$ringnr))])

#Number of males and females individual breeding seasons
table(d3$adsex)

##Number of individuals per island
table(d3$name[-which(duplicated(d3$ringnr))])

##Number of individual breeding season per island
table(d3$name)

###Number of individuals that were recorded breeding per year of birth in each island 
table(d3$name, d3$firstyear)

###Number of individuals that were recorded breeding per year of death in each island 
table(d3$name, d3$lastyear)

###Number of individuals that were recorded breeding per year in each island 
table(d3$name, d3$year)
```

dI is a data set that contains the life history metrics for each individual. These metrics were calculated using a subset of the data in d3.
```{r Descriptive statistics data set 2}

##Number of individuals
length(levels(droplevels(as.factor(dI$ringnr))))

##Number of males and females
table(dI$sex)

##Number of individuals per island
table(dI$name)

##Number of individuals that were recorded breeding per year of birth in each island 
table(dI$name, dI$firstyear)

##Number of individuals that were recorded breeding per year in each island 
table(dI$name, dI$lastyear)

```

dFY2 is data set that contains the average mean age at reproduction for each island in each year,
```{r Descriptive statistics data set 3}
table(droplevels(as.factor(dFY2$newflok)))
table(dFY2$newflok, dFY2$year)
min(dI$GT)
max(dI$GT)
```

The following code can be used to replicate the analyzes presented in table 1.
```{r Analysis table 1, cache=TRUE}
#Note that flok is the code for population.
#Column 1
model_GTA <- brm(GT ~ 1 + sex + (1|animal) + (1|flok) + (1|firstyear),    data = dI,
                  family = gaussian(),
                  cov_ranef = list(animal = A),
                  chains = 3,
                  cores = 3,
                  iter = 3000,
                  thin=3)
summary(model_GTA)

##Estimating heritability and evolvability
posterior_brms <- posterior_samples(model_GTA, pars = c("sd_animal", "sd_flok", "sigma","sd_firstyear", "Intercept"))

h2_brms  <- (posterior_brms[,1]^2/(posterior_brms[,1]^2 + posterior_brms[,2]^2 + posterior_brms[,3]^2 + posterior_brms[,4]^2))*100

round(mean(h2_brms),2)
round(quantile(h2_brms, c(0.025,0.975)),2)

e<-(posterior_brms[,1]^2/posterior_brms[,5]^2*100)
round(mean(e),2)
round(quantile(e, c(0.025, 0.975)),2)

#Column 2
mod.GT<-brm(lGT~sex + lBM +(1|flok) + (1|firstyear), data=dIM,  chains = 3, cores = 3)
summary(mod.GT)

#Column 3
mod.LRS<-brm(LRS ~ GT +sex + (1|flok) + (1|firstyear), data=dI,  chains = 3, cores = 3)
summary(mod.LRS)

#Column 4
mod.Lambda<-brm(lambda ~ GT +sex + (1|flok)  + (1|firstyear), data=dI,  chains = 3, cores = 3)
summary(mod.Lambda)


```

The following code can be used to replicate the analyzes presented in table S2.
```{r Analysis table S2, cache=TRUE}
#Column 1
model_GTA2 <- brm(GT ~ 1 + sex + (1|animal),
                  data = dI,
                  family = gaussian(),
                  cov_ranef = list(animal = A),
                  chains = 3,
                  cores = 3,
                  iter = 3000,
                  thin=3)

summary(model_GTA2)

posterior_brms <- posterior_samples(model_GTA2, pars = c("sd_animal", "sigma", "Intercept"))

h2_brms  <- (posterior_brms[,1]^2 / (posterior_brms[,1]^2 + posterior_brms[,2]^2))*100
round(mean(h2_brms),2)
round(quantile(h2_brms, c(0.025,0.975)),2)

e<-(posterior_brms[,1]^2/posterior_brms[,3]^2*100)
round(mean(e),2)
round(quantile(e, c(0.025, 0.975)),2)

#Column 2
model_lGTA <- brm(lGT ~ 1 + sex + lBM + (1|animal) + (1|flok) + (1|firstyear),
                  data = dIM,
                  family = gaussian(),
                  cov_ranef = list(animal = A),
                  chains = 3,
                  cores = 3,
                  iter = 3000,
                  thin=3)

summary(model_lGTA)

#Column 3
model_GTALN <- brm(GT ~ 1 + sex + (1|animal) + (1|flok) + (1|firstyear),
                  data = dI,
                  family = lognormal(),
                  cov_ranef = list(animal = A),
                  chains = 3,
                  cores = 3,
                  iter = 3000,
                  thin=3)

summary(model_GTALN)

#Column 4
mod.LRS2<-brm(LRS ~ GT +sex + (1|flok) + (1|firstyear), data=dI,  chains = 3, cores = 3, family=poisson())
summary(mod.LRS2)

#Column 5
mod.Lambda2<-brm(lambda ~ GT +sex + (1|flok)  + (1|firstyear), data=dI,  chains = 3, cores = 3, family=lognormal())
summary(mod.Lambda2)


```

The following code can be used to replicate the analyzes presented in table 2.
```{r Analysis table 2: Models age dep rep and surv, cache=TRUE}
#Column 1
mod.recruits<-brm(totalrecruits ~ age*gensex + agesq*gensex + mean.pop + rel.pop + (1|ringnr) + (1|laflok) +  (1|year), data=d3, chains = 3, cores = 3, iter=5000,family=negbinomial())
summary(mod.recruits)

##Note that the presented model in the paper is in a CMR framework (see below).
mod.surv<-brm(survival ~ age*gensex + agesq*gensex + mean.pop + rel.pop + (1|ringnr) + (1|laflok) +  (1|year), data=d3, chains = 3, iter=3000, cores = 3, family=bernoulli())
summary(mod.surv)


mod.recruits2<-brm(totalrecruits ~ age2*gensex + mean.pop + rel.pop +  (1|ringnr) + (1|laflok) +  (1|year), data=d4, chains = 3, cores = 3, iter=3000,family=negbinomial())
summary(mod.recruits2)


mod.surv2<-brm(survival ~ age2*gensex + mean.pop + rel.pop + (1|ringnr) + (1|laflok) +  (1|year), data=d4, chains = 3, iter=3000, cores = 3, family=bernoulli())
summary(mod.surv2)

mod.surv3<-brm(survival ~ age*gensex + mean.pop + rel.pop + (1|ringnr) + (1|laflok) +  (1|year), data=d3, chains = 3, iter=3000, cores = 3, family=bernoulli())
summary(mod.surv3)
```

```{r Mark-recapture model prepare data}

get.first <- function(x) min(which(x!=0))
dc2<-read.csv("/home/yi/Desktop/Desktop2021/HelgelandCMRcombined2ad_2.csv", sep=";")
dR2<-d3[(d3$firstyear+1)>1998 & (d3$firstyear+1)<2012, c("ringnr", "gensex", "laflok", "mean.pop", "age", "year")]

dR1<- spread(dR2, year, age)
dxxx<-merge(dc2, dR1)
dxx<-dxxx[apply(dxxx[c(9:23)],1,sum)!=0,]

CH<-dc<-dxx[,c(9:24)]
dA<-dxx[,32:ncol(dxx)]


dP2<-d3[-which(duplicated(d3$flok_year)),c("laflok", "year", "rel.pop")]
dP1<- as.matrix(spread(dP2, year, rel.pop)[,-1])
dP1[is.na(dP1)]<-0
dP<-matrix(NA,8,15)
dP[]<-dP1[]
sex<-as.numeric(dxx$gensex)-1
flok<-as.numeric(as.factor(dxx$laflok))
mean.pop<-dxx$mean.pop


f<-apply(dc, 1, get.first)

x<-matrix(NA,nrow(dc), ncol(dc)-1)
for(i in 1:nrow(x)){
x[i,f[i]:ncol(x)]<-1:length(f[i]:ncol(x))
x[i,f[i]]<-1
}

FY<-dP
FY[]<-1:120
x[is.na(x)]<-0

max(x)
stan_data <- list(y =CH ,  nind = dim(CH)[1], n_occasions =
                    dim(CH)[2], flok=flok, nflok=max(flok), xl=x, sex=sex, mean_pop=mean.pop, rel_pop=dP, FY=FY, nFY=120, max_age=max(x))

cjs.init.z <- function(ch,f){
  for (i in 1:dim(ch)[1]){
    if (sum(ch[i,])==1) next
    n2 <- max(which(ch[i,]==1))
    ch[i,f[i]:n2] <- NA
  }
  for (i in 1:dim(ch)[1]){
    ch[i,1:f[i]] <- NA
  }
  return(ch)
}

#Initial values
###if gets stuck repeaat initial
inits <- function() list(y = cjs.init.z(CH, f), mean_p = runif(1, 0, 1),
                         sigmaI_phi = runif(1, 0, 1),
                         sigmaFY_p = runif(1, 0, 1))

#Parameters monitored

params <- c("mean_phi", "mean_p", "sigmaFY_p", "sigmaF_phi",  "sigmaY_phi", "sigmaI_phi", "s_phi", "B","Bq", "Bs","Bqs", "mu_phi", "dr", "dm")
## MCMC settingsl
ni <- 5000
nt <- 15
nc <- 3


## Call Stan from R
cjs_temp_raneff2 <- stan("cjs_temp_raneff2.stan",
                        data = stan_data, init = inits, pars = params,
                        chains = nc, iter = ni, thin = nt,
                        cores=3)

                  # # Summarize posteriors 
print(cjs_temp_raneff2, digits = 2)
```

The following code can be used to replicate the analyzes presented in table 3.
```{r Analysis table 3, cache=TRUE}
mod.meanAgeR1<-brm(meanAgeR~  gensex * meanW +  (1|flok) + (1|year), data=dFY2, family=gaussian(),
                  chains = 3,
                  cores = 3)
summary(mod.meanAgeR1)

mod.meanAgeR2<-brm(meanAgeR~ gensex + mean.pop + gensex*rel.pop +  (1|flok) + (1|year), data=dFY2, family=gaussian(),
                  chains = 3,
                  cores = 3)
summary(mod.meanAgeR2)
```

The following code can be used to replicate the analyzes presented in table S3.
```{r Analysis table S3, cache=TRUE}
#Column 1
mod.meanAgeR1LN<-brm(meanAgeR~  gensex2 * meanW +  (1|flok) + (1|year), data=dFY2, family=lognormal(),
                  chains = 3,
                  cores = 3)
summary(mod.meanAgeR1LN)

#Column 2
mod.meanAgeR2LN<-brm(meanAgeR~ gensex2 + mean.pop + gensex2*rel.pop +  (1|flok) + (1|year), data=dFY2, family=lognormal(),
                  chains = 3,
                  cores = 3)
summary(mod.meanAgeR2LN)

#Column 3
mod.meanAgeRB<-brm(meanAgeR~  gensex2 * meanW + meanAge +  (1|flok) + (1|year), data=dFY2, family=gaussian(),
                  chains = 3,
                  cores = 3)
summary(mod.meanAgeRB)


#Column 4
mod.meanAgeRB2<-brm(meanAgeR~  mean.pop + gensex2*rel.pop + meanAge+ (1|flok) + (1|year), data=dFY2, family=gaussian(),
                  chains = 3,
                  cores = 3)
summary(mod.meanAgeRB2)
```

Code to produce figure 1.
```{r Figure 1: Age dep rep}

jpeg("/home/yi/Dropbox/GT/Final/Figure1.jpeg",width = 6000, height = 4000, res=600)

par(mfrow=c(2,3))

dSR<-d3f %>% group_by(adsex, agen) %>% summarize(sumRE=mean(totalrecruits, na.rm=TRUE))
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE, na.rm=TRUE)
dSR<-dSR[1:7,]

plot(dSR$sumREp~dSR$agen, type="l",  ylim=c(0,0.5), ylab="# of recruits/individual", xlab="Age of mother", lwd=2, cex.lab=1.2, yaxt="n")
axis(2, seq(0,0.5, by=0.1), seq(0,0.5, by=0.1), las=2)

mtext("A)",3, 0.6, at=1, las=1)

dSR<-d3f %>% group_by(flok2, adsex, agen) %>% summarize(sumRE=mean(totalrecruits))
for(i in 1:max(d4$flok2)){
dSR.tmp<-dSR[dSR$flok2==i,]
dSR.tmp$sumREp<-dSR.tmp$sumRE/sum(dSR.tmp$sumRE, na.rm=TRUE)
points(dSR.tmp$sumREp~dSR.tmp$agen, type="l", col="lightgray")
}
dSR<-d3f %>% group_by(adsex, agen) %>% summarize(sumRE=mean(totalrecruits, na.rm=TRUE))
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE, na.rm=TRUE)
dSR<-dSR[1:7,]
points(dSR$sumREp~dSR$agen, type="l", lwd=2)

dSR<-d3f %>% group_by(adsex, agen) %>% summarize(sumRE=sum(totalrecruits, na.rm=TRUE))
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE, na.rm=TRUE)
dSR<-dSR[1:7,]


plot(dSR$sumREp~dSR$agen, type="l", ylim=c(0,0.7), ylab="Proportions of recruits", xlab="Age of mother", lwd=2, cex.lab=1.2, yaxt="n")
axis(2, seq(0,0.7, by=0.1), seq(0,0.7, by=0.1), las=2)

mtext("B)",3, 0.6, at=1, las=1)

dSR<-d3f %>% group_by(flok2, adsex, agen) %>% summarize(sumRE=sum(totalrecruits))
dSR<-as.data.frame(dSR[complete.cases(dSR$flok2),])

for(i in 1:max(d4$flok2)){
dSR.tmp<-dSR[dSR$flok2==i,]
dSR.tmp$sumREp<-dSR.tmp$sumRE/sum(dSR.tmp$sumRE, na.rm=TRUE)
points(dSR.tmp$sumREp~dSR.tmp$age, type="l", col="lightgray")
}
dSR<-d3f %>% group_by(adsex, age) %>% summarize(sumRE=sum(totalrecruits, na.rm=TRUE))
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE, na.rm=TRUE)
dSR<-dSR[1:7,]

points(dSR$sumREp~dSR$agen, type="l", lwd=2)


dSR<-as.data.frame(table(d3f$agen))
dSR$Freq2<-dSR$Freq/sum(as.numeric(dSR$Freq))
plot(dSR$Freq2~as.numeric(dSR$Var1),  type="l",  ylab="Proportion of females", xlab="Age of females", lwd=2, ylim=c(0,0.7), cex.lab=1.2, yaxt="n")
axis(2, seq(0,0.7, by=0.1), seq(0,0.7, by=0.1), las=2)

mtext("C)",3, 0.6, at=1, las=1)

dSR<-as.data.frame(table(d3f$agen, d3f$flok2))
for(i in 1:max(d4$flok2)){
dSR.tmp<-dSR[dSR$Var2==i,]
dSR.tmp$Freq2<-dSR.tmp$Freq/sum(as.numeric(dSR.tmp$Freq))
points(dSR.tmp$Freq2~as.numeric(dSR.tmp$Var1),  type="l",  col="lightgray")
}

dSR<-as.data.frame(table(d3f$agen))
dSR$Freq2<-dSR$Freq/sum(as.numeric(dSR$Freq))
points(dSR$Freq2~as.numeric(dSR$Var1), type="l", lwd=2)


dSR<-d3m %>% group_by(adsex, agen) %>% 
summarize(sumRE=mean(totalrecruits))
dSR<-dSR[1:7,]
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE)
plot(dSR$sumREp~dSR$agen, type="l", ylim=c(0,0.5), ylab="# of recruits/individual", xlab="Age of father", lwd=2, cex.lab=1.2, yaxt="n")
axis(2, seq(0,0.5, by=0.1), seq(0,0.5, by=0.1), las=2)

mtext("D)",3, 0.6, at=1, las=1)

dSR<-d3m %>% group_by(flok2, adsex, agen) %>% summarize(sumRE=mean(totalrecruits))
dSR<-as.data.frame(dSR[complete.cases(dSR$flok2),])
for(i in 1:max(d4$flok2)){
dSR.tmp<-dSR[dSR$flok2==i,]
dSR.tmp$sumREp<-dSR.tmp$sumRE/sum(dSR.tmp$sumRE)
points(dSR.tmp$sumREp~dSR.tmp$agen, type="l", col="lightgray")
}

dSR<-d3m %>% group_by(adsex, agen) %>% 
summarize(sumRE=mean(totalrecruits))
dSR<-dSR[1:7,]
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE)
points(dSR$sumREp~dSR$agen, type="l", lwd=2, cex.lab=1.2)


dSR<-d3m %>% group_by(adsex, agen) %>% summarize(sumRE=sum(totalrecruits))
dSR<-dSR[1:7,]
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE)
plot(dSR$sumREp~dSR$agen, type="l",  ylim=c(0,0.7), ylab="Proportions of recruits", xlab="Age of sire", lwd=2, cex.lab=1.2, yaxt="n")
axis(2, seq(0,0.7, by=0.1), seq(0,0.7, by=0.1), las=2)

mtext("E)",3, 0.6, at=1, las=1)

dSR<-d3m %>% group_by(flok2, adsex, agen) %>% summarize(sumRE=sum(totalrecruits))
dSR<-as.data.frame(dSR[complete.cases(dSR$flok2),])
for(i in 1:max(d4$flok2)){
dSR.tmp<-dSR[dSR$flok2==i,]
dSR.tmp$sumREp<-dSR.tmp$sumRE/sum(dSR.tmp$sumRE)
points(dSR.tmp$sumREp~dSR.tmp$age, type="l", col="lightgray")
}
dSR<-d3m %>% group_by(adsex, agen) %>% summarize(sumRE=sum(totalrecruits))
dSR<-dSR[1:7,]
dSR$sumREp<-dSR$sumRE/sum(dSR$sumRE)

points(dSR$sumREp~dSR$agen, type="l", lwd=2)

dSR<-as.data.frame(table(d3m$agen))
dSR$Freq2<-dSR$Freq/sum(as.numeric(dSR$Freq))
plot(dSR$Freq2~as.numeric(dSR$Var1),  type="l",  ylab="Proportion of males", xlab="Age of males", lwd=2, ylim=c(0,0.7), cex.lab=1.2, yaxt="n")
axis(2, seq(0,0.7, by=0.1), seq(0,0.7, by=0.1), las=2)

mtext("F)",3, 0.8, at=1, las=1)
dSR<-as.data.frame(table(d3m$agen, d3m$flok))
for(i in levels(as.factor(d3m$flok))){
dSR.tmp<-dSR[dSR$Var2==i,]
dSR.tmp$Freq2<-dSR.tmp$Freq/sum(as.numeric(dSR.tmp$Freq))
points(dSR.tmp$Freq2~as.numeric(dSR.tmp$Var1),  type="l",  col="lightgray")
}
dSR<-as.data.frame(table(d3m$agen))
dSR$Freq2<-dSR$Freq/sum(as.numeric(dSR$Freq))
points(dSR$Freq2~as.numeric(dSR$Var1), type="l", lwd=2)


dev.off()
```

Code to produce figure 2.
```{r Figure 2: Plot Growth and mean age}
jpeg("/home/yi/Dropbox/GT/Final/Figure1.jpeg",width = 4000, height = 2000, res=600)

dFY2F<-dFY2[dFY2$gensex=="f", ]
dFY2M<-dFY2[dFY2$gensex=="m", ]

par(mfrow=c(1,2), mar=c(4,3,2,1))

plot(dFY2F$meanAgeR+1~dFY2F$meanW, ylab="", xlab="", yaxt="n", xlim=c(0,1.8), ylim=c(0.5,5.2), col="darkgray")
axis(2, 0:5, 0:5, las=2)
mtext("Mean age of mothers",2,2, cex=0.8)
mtext("Mean fitness",1,2, cex=0.8)
mtext("A)",2,-0.5, at=5.7, las=2)
mod<-lmer(meanAgeR+1~meanW +(1|flok) + (1|year), data=dFY2F)
smod<-sim(mod,1000)
x<-seq(0,1.8, by=0.01)
y<-matrix(NA, 1000, length(x))
for(i in 1:1000){
y[i,]<-smod@fixef[i,1] + smod@fixef[i,2]*x   
}
l<-apply(y,2,quantile, 0.025)
u<-apply(y,2,quantile, 0.975)
m<-apply(y,2,mean)
points(m~x, type="l")
points(u~x, type="l", lty=2)
points(l~x, type="l", lty=2)

plot(dFY2M$meanAgeR + 1~dFY2M$meanW, ylab="", xlab="", yaxt="n", xlim=c(0,1.8), ylim=c(0.5,5.2), col="darkgray")
axis(2, 0:5, 0:5, las=2)
mtext("Mean age of fathers",2,2, cex=0.8)
mtext("Mean fitness",1,2, cex=0.8)
mtext("B)",2,-0.5, at=5.7, las=2)
mod<-lmer(meanAgeR+1~meanW +(1|flok) + (1|year), data=dFY2M)
smod<-sim(mod,1000)
x<-seq(0,1.8, by=0.01)
y<-matrix(NA, 1000, length(x))
for(i in 1:1000){
y[i,]<-smod@fixef[i,1] + smod@fixef[i,2]*x   
}
l<-apply(y,2,quantile, 0.025)
u<-apply(y,2,quantile, 0.975)
m<-apply(y,2,mean)
points(m~x, type="l")
points(u~x, type="l", lty=2)
points(l~x, type="l", lty=2)

dev.off()
```

Code to produce figure S1.
```{r Figure S1}
mod.recruits<-glm(totalrecruits ~ age*gensex + agesq*gensex + mean.pop + rel.pop, data=d3, family=poisson)

mod.recruits2<-glm(totalrecruits ~ age2*gensex + mean.pop + rel.pop, data=d4, family=poisson)

mod.surv<-glm(survival ~ age*gensex + agesq*gensex + mean.pop + rel.pop, data=d3, family=binomial)
summary(mod.surv)

mod.surv2<-glm(survival ~ age2*gensex +  mean.pop + rel.pop, data=d4, family=binomial)
summary(mod.surv2)

age<-seq(0,6, by=0.1)
B<-coef(mod.recruits)
B2<-coef(mod.surv)
B3<-coef(mod.recruits2)
B4<-coef(mod.surv2)

dSR<-d3f %>% group_by(age) %>% summarize(sumRE=mean(totalrecruits, na.rm=TRUE),
          surv=mean(survival, na.rm=TRUE))
dSR<-dSR[1:7,]

jpeg("/home/yi/Dropbox/GT/Resubmission/Resubmission3/FigureS1.jpeg", width = 1800, height = 1200, res=200)
par(mfrow=c(2,2))
plot(dSR$sumRE~dSR$age, type="p", ylab="# of recruits/individual", xlab="Age of female", lwd=2, cex.lab=1.2, ylim=c(0.2,1), cex=1, pch=19, xaxt="n")
mtext("A)",3, 0.6, at=1, las=1)
axis(1, 0:6, 1:7)

y=exp(B[1] + ((B[2]) * age) + (B[4])*age^2  + B[5]*mean(d3$mean.pop) + B[6]*mean(d3$rel.pop)) 
points(y~age, type="l")

y2=c(exp(B3[1] + B3[9]*mean(d3$mean.pop) + B3[10]*mean(d3$rel.pop)), exp(B3[1] + B3[9]*mean(d3$mean.pop) + B3[10]*mean(d3$rel.pop) + B3[2:7]))

points(y2~c(0:6), col="red", cex=1.5)

plot(dSR$surv~dSR$age, type="p", ylab="Survival (p)", xlab="Age of female", lwd=2, cex.lab=1.2, ylim=c(0.2,0.8), pch=19, xaxt="n")
mtext("B)",3, 0.6, at=1, las=1)
axis(1, 0:6, 1:7)

y=invlogit(B2[1] + ((B2[2]) * age) + (B2[4])*age^2  + B2[5]*mean(d3$mean.pop) + B2[6]*mean(d3$rel.pop)) 
points(y~age, type="l")

y2=c(invlogit(B4[1] + B4[9]*mean(d3$mean.pop) + B4[10]*mean(d3$rel.pop)), invlogit(B4[1] + B4[9]*mean(d3$mean.pop) + B4[10]*mean(d3$rel.pop) + B4[2:7]))

points(y2~c(0:6), col="red", cex=1.5)

dSR<-d3m %>% group_by(age) %>% 
summarize(sumRE=mean(totalrecruits, na.rm=TRUE),
          surv=mean(survival))

dSR<-dSR[1:7,]
plot(dSR$sumRE~dSR$age, type="p", ylab="# of recruits/individual", xlab="Age of male", lwd=2, cex.lab=1.2, ylim=c(0.2,1), xaxt="n", pch=19)
mtext("C)",3, 0.6, at=1, las=1)
axis(1, 0:6, 1:7)

y=exp(B[1] + B[3] + ((B[2] + B[7]) * age) + (B[4] + B[8])*age^2  + B[5]*mean(d3$mean.pop) + B[6]*mean(d3$rel.pop)) 
points(y~age, type="l")

y2=c(exp(B3[1] + B3[8] + B3[9]*mean(d3$mean.pop) + B3[10]*mean(d3$rel.pop)), exp(B3[1] +  B4[8]   + B3[11:16] + B3[9]*mean(d3$mean.pop) + B3[10]*mean(d3$rel.pop)))
points(y2~c(0:6), col="red", cex=1.5)


plot(dSR$surv~dSR$age, type="p", ylab="Survival (p)", xlab="Age of male", lwd=2, cex.lab=1.2, ylim=c(0.2,0.8), xaxt="n", pch=19)
mtext("D)",3, 0.6, at=1, las=1)
axis(1, 0:6, 1:7)

y=invlogit(B2[1] + B2[3] + ((B2[2] + B2[7]) * age) + (B2[4] + B2[8])*age^2  + B2[5]*mean(d3$mean.pop) + B2[6]*mean(d3$rel.pop)) 
points(y~age, type="l")

y2=c(invlogit(B4[1] + B4[8] + B4[9]*mean(d3$mean.pop) + B4[10]*mean(d3$rel.pop)), invlogit(B4[1] +  B4[8] + B4[9]*mean(d3$mean.pop) + B4[10]*mean(d3$rel.pop) + B4[2:7] + B4[11:16]))

points(y2~c(0:6), col="red", cex=1.5)

dev.off()
```

